---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RpCS

<!-- badges: start -->
<!-- badges: end -->

Coronavirus has spread through most countries in the world. Xi (2020) developed a novel Monte Carlo simulation procedure for modeling Covid19 spread over time. In this package, we implement the simulation, recreate Fig 2 which explores active infections over a number of days under a variety of parameter settings (see paper), and additionally we incorporate a daily hospitalization rate into the simulation.

## Installation

You can install the released version of RpCS from [CRAN](https://CRAN.R-project.org) with:

``` r
library(devtools)
library(stats)
library(parallel)
library(foreach)
library(doParallel)
library(fame)
install_github("egetzen5/RpCS")
library(RpCS)
```

## Example


```{r active_infections, eval=FALSE}
Sim_Active_Infections(max_iter=1000)
```


```{r daily_hospitalizations, eval=FALSE}
Sim_Daily_Hospitalizations(max_iter=1000)
```

